---
title: "Introduction to SC19037"
author: '19037'
date: "2020/01/03"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to SC19037}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__SC19037__ is a simple R package developed to realize some computation. Three functions are considered, namely, _Complex_det_ (compute the determinant of a complex matrix), _k_choose_(Selecting the optimal ridge regression parameters by GCV and GIC) and _LLN_and_CTL_(Verify the Law of Large Numbers and the Central Limit Theorem by figure).


## Benchmarking _Complex_det_

The source R code for _Complex_det_ is as follows:
```{r}  
# compute the determinant of a complex matrix
Complex_det <- function(x){
  if (length(x) == 1){
    return (x)
  }
  c <- numeric(nrow(x))
  det <- 0
  n <- nrow(x)
  for (i in 1:n){
    y <- x[-i,-1]
    c[i] <- (-1)^(i+1) * (x[i,1] %*% Complex_det(y))
    det <- det + c[i]
  }
  return(det)
}
```

Here, a example by using this function:
```{r}
x <- matrix(c(1+1i,2,3+4i,2i,3+7i,1-3i,2+4i,-1i,9),3,3)
Complex_det(x)
```


## Benchmarking _k_choose_

The source R code for _k_choose_ is as follows:
```{r}
# by GCV
k_choose1 <- function(X, Y, kmax, N){
  K <- seq(0, kmax, kmax/N)
  GCV <- numeric(0)
  for (k in K) {
    # get the reponse variable with parameter k
    Y_k <-  X %*% solve(t(X) %*% X + k * diag(ncol(X))) %*% t(X) %*% Y
    # compute the value of generalized cross validation with parameter k
    GCV_k <- sum((Y - Y_k)^2) / (nrow(X) - sum(matrix((svd(X)$d)^2/((svd(X)$d)^2 
              + rep(k, rep(length(svd(X)$d), 1))), length(svd(X)$d))))^2
    GCV <- c(GCV, GCV_k)
  }
  # return the optimal parameter k which makes the GCV minimum
  return (K[which.min(GCV)])
}
```

```{r}
# by GIC
k_choose2 <- function(X, Y){ 
  beta <- solve(t(X) %*% X) %*% t(X) %*% Y
  ng <- length(Y)
  numzero <- length(which(beta == 0))
  lenbeta <- length(beta)
  temp <- 0
  for(i in 1:ng)
  {
    temp <- temp + 1/ng * (Y[i] - sum(X[i,] * beta))^2   
  }
  GIC <- log(temp) + (lenbeta - numzero - 1) * log(log(ng))/ng * log(max(lenbeta, ng))
  return(GIC)
}
```

As following, give a example:
```{r}
data <- read.table("E:/Rcpp/data.txt", header = TRUE)
x <- as.matrix(data[,2:21])
y <- data[,1]
k_best1 <- k_choose1(x, y, kmax = 2, N = 2000)
k_best1
k_best2 <- k_choose2(x, y)
k_best2
```

We can also compare it with the parameter getting by existing package.
```{r}
library(MASS)
select(lm.ridge(y~x, data = data, lambda = seq(0,2,0.001)))
```


## Benchmarking _LLN_and_CTL_

The source R code for _LLN_and_CTL_ is as follows:
```{r}
# Verify the Law of Large Numbers
LLN <- function(r, mean, n){
  y <- numeric(n)
  for (i in 1:n){
    y[i] <- mean(sample(r,i,replace=TRUE))
  }
  lln_data <- data.frame(1:n, y)
  plot(lln_data, xlab = "Sample Size", ylab = "Average Value", col=" light green")
  abline(h = mean, col = "red")
}
```

```{r}
# Verify the Central Limit Theorem
CLT <- function (r, parameter, mean, var, n, N=1000){
  
  if (length(parameter) == 1){
    for (i in n) {
      x <- matrix(r(i*N, parameter), nrow = N, ncol = i)
      x <- (apply(x, 1, sum) - i * mean )/(sqrt(i) * sqrt(var))
      hist(x, col = 'light yellow', probability = T, main = paste("n = ",i),
           ylim = c(0, max(0.5, density(x)$y)))
      lines(density(x), col='red', lwd = 3)
      curve(dnorm(x), col='blue', lwd = 3, add = T)
    }
  }
  
  if (length(parameter) == 2){
    p1 <- parameter[1]
    p2 <- parameter[2]
    for (i in n) {
      x <- matrix(r(i*N, p1, p2 ), nrow = N, ncol = i) 
      x <- (apply(x, 1, sum) - i * mean )/(sqrt(i) * sqrt(var))
      hist(x, col = 'light yellow', probability = T, main = paste("n = ",i),
           ylim = c(0, max(0.5, density(x)$y)))
      lines(density(x), col='red', lwd = 3)
      curve(dnorm(x), col='blue', lwd = 3, add = T)
    }
  }
}
```

Using this function to verify some distribution.

1. bernoulli distribution
```{r}
# Verify the Law of Large Numbers
n <- 1000
LLN(rbinom(n, 1, 0.3), 0.3, n)
```

```{r}
# Verify the Central Limit Theorem
n <- c(1,10,30,100)
CLT(rbinom, parameter = c(1, 0.3), 0.3, 0.21, n)
```


2. possison distribution
```{r}
# Verify the Law of Large Numbers
n <- 1000
LLN(rpois(n, 1), 1, n)
```

```{r}
# Verify the Central Limit Theorem
n <- c(1,10,30,100)
CLT(rpois, parameter = 1, 1, 1, n)
```


3. uniform distribution
```{r}
# Verify the Law of Large Numbers
n <- 1000
LLN(runif(n,0,1),0.5,n)
```

```{r}
# Verify the Central Limit Theorem
n <- c(1,10,30,100)
CLT(runif, parameter = c(0,1), 0.5, 1/12, n)
```


4. exponential distribution
```{r}
# Verify the Law of Large Numbers
n <- 1000
LLN(rexp(n, 1), 1, n)
```

```{r}
# Verify the Central Limit Theorem
n <- c(1,10,30,100)
CLT(rexp, parameter = 1, 1, 1, n)
```